The brightness and spatial distributions of terrestrial radio sources

### 2013-07-16 articles/Article-RFI-distribution/article-rfi-distribution.tex
Fixing final comment by referee

@@

\editmark{It is common knowledge that in a uniform Euclidian Universe source counts behave like power-law distributions. For sources on a flat surface, the power law will have a -2 exponent}. We will derive this expected intrinsic source distribution for interfering radio sources. After that, we will analyse the issues that arise when measuring the distribution by counting samples.

@@

>>>>

% To make Dutch ``tussenvoegsels'' work correctly in Latex such as ``de Bruyn'', we use this command
% It fixes ordering and uppercases.
% In text, it should be written with uppercase, as in ``De Bruyn''
\DeclareRobustCommand{\TUSSEN}[3]{#2}

@@

It is common knowledge that in a uniform Euclidian Universe source counts behave like power-law distributions. \editmark{The differential distribution for sources on a flat surface is a power law with -2 exponent}. We will derive this expected intrinsic source distribution for interfering radio sources. After that, we will analyse the issues that arise when measuring the distribution by counting samples.

@@

% To make Dutch ``tussenvoegsels'' work correctly in Latex such as ``de Bruyn'', we use this command
% In bibliography, it should be written with lowercase, as in ``de Bruyn''
\DeclareRobustCommand{\TUSSEN}[3]{#3}
